---
title: "DataCleaning"
author: "Lu-K Gautier"
date: '2022-11-09'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set Up environments
```{r setup, include=FALSE}

cat("\014") # clear console
rm(list=ls()) # clear workspace

# Load packages

# 4 lines : Installs (if necessary) and loads the packages you enter in the 1st row
# 1st row : Creates a list of packages names that you want to use in the script (there is virtually no limit in how much package you can put here)
# 2nd row : Creates a list of packages that have not been installed yet (new packages)
# 3rd row : Installs the new packages
# 4th row : Loads all the listed packages
list.of.packages <- c("dplyr", "emmeans", "tidyverse", "readr", "psych", "lmerTest")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
invisible(lapply(list.of.packages, require, character.only = TRUE))

rm(list=ls()) # clear workspace

set.seed(42) # set overall random seed for reproducibility
```


# Aim of the script : 
Open and prepare data from the ThreatControlability project to run analysis.


# Build the dataframe

## Experiment dataframe
### Open files

```{r}
# Create a file containing each file name present in the folder
Filelist <- list.files(path = "Data/experiment_data/") 
# Give the number of file in the folder (it's also the number of participants)
Nb_Ppt<- length(Filelist)

List = list() # Create an empty list
df <- data.frame() # Create an empty dataframe

# A loop for open all the particpant data in a unique dataframe
for (i in Filelist) {
  no_col <- max(count.fields(paste("Data/experiment_data/",i, sep = ""), sep = " ")) # Count the number of column in each datafile
  
  tmp<- read.table(paste("Data/experiment_data/",i, sep = ""),sep=" ",fill=TRUE,header = F,col.names=c(1:no_col)) # Read the datafile
  
  tmp$Ppt <- i # Add the name of the participant to the dataframe
  tmp$response_id <- length(List)+1 # Add the participant ID to the dataframe

  df<- rbind(df,tmp) # Add the last file read to the final dataframe
  List[[length(List)+1]] = i # Inncrease the participant ID for reading the next file
}

# Transform participant ID in a factor
df$response_id <- factor(df$response_id)
# Give the number of participant
Nb_level<- nlevels(df$response_id)

# Is the number of participants in the final dataframe match the original number of files
ifelse(identical(Nb_Ppt,Nb_level)==TRUE, ("The number of participants in the final dataframe match the number of files"),("Warning: The number of participants do not match the number of files"))

rm(list=setdiff(ls(), c("df"))) # clear workspace except the data frame
```

###Rename variables

- Ppt_Response_Nb: The response given by the participant in terms of number (1=g, 2=b, 3=h, 4=y)

- Ppt_Response: The response given by the participant (g, b, h or y) in the location task

- Catego_Key_Response: the theoretical correct response key for the same task with a 

categorization instruction (b or n)

- Key_Response_Nb: The correct response for the localization task in terms of number (1=g, 2=b, 3=h, 4=y)

- Response_Status: Participant Response status : 1=Correct answer, 2=Wrong answer, 3=No response (>1500ms)

- Target_Position: The localisation of the target positition (left, right, top, bottom)

- Target_Type: Which target the participants should respond to (X or =). The target type is randomly assign for each trial (within-subject)

- Target_Color: The color of the target participants should response to. This color is assign to participants (between-subject) during instructions and stay the same during all the task

- Cueing_Status: Trial type in terms of cueing validity. Same = Cue and target appear at the same localization ; Different = Cue and target appear at different localizations ; NoLocation = No cue validity since all cues are white 

- Cueing_Validity: Rename "Cueing_Status" to match the cueing validity standards (Valid, Invalid or NoValidity)

- Cue_Position: The position of the cue (left, bottom, right, top or NoCue)

- Cue_Color: Color of the cue (red, green or white)

- Congruency: Congruency (in terms of color) between cue and target. Congruent = same color between target and cue ; Incongruent = Different colors between target and cue ; NoCongruency = No congruency because all cues are white

- RT: Response time for each trial

- Blockname: Name of the block the participant is completing :
  - Training_Red/Training_Green: Training block = 20 trials of practice
  - Control_Red/Control_Green: Control block = the spatial cueing task in its original conceptualisation (144 trials)
  - TrialXRedThreat/TrialXGreenThreat: Threat block = the spatial cueing task in which participants hear screams during the task  (144 trials)
  - TrialXRedToon/TrialXGreenToon: Toon block = the spatial cueing task in which participants hear vocalizations during the task  (144 trials)
In these three blocks of trials, the distribution of trials is as follows:
        - No-Congruency = 48
        - Congruent Valid = 12
        - Congruent Invalid = 36
        - Incongruent Valid = 12
        - Incongruent Invalid = 36
  - ScaleControl: Anxiety ratings after the control block
  - ScaleThreat: Anxiety ratings after the Threat block
  - ScaleToon: Anxiety ratings after the Toon block
  - TrialScream: A screams happens
  - TrialToon: A vocalization happens
  
- Taskname: The name of the task completed by the participant for this specific trial

- Order: The order of task completion. In this specific experiment all participants are exposed to the "Threat then Toon" Blockorder. 1 = ControlRed then ThreatRed then ToonRed Blocks ; 2 = ControlGreen then ThreatGreen then ToonGreen Blocks

- Blockorder: The order of task completion (ThreatFirst_Red or ThreatFirst_Green)

- SOA: Duration between the fixation point and the cue happening in ms (1000ms, 1100ms, 1200ms, 1300ms, 1400ms)

- Sound_Nb: The sound number that the participant hear. 
  - 3 = ExpF1
  - 4 = ExpF2
  - 5 = ExpF3
  - 6 = ExpM1
  - 7 = ExpM2
  - 8 = ExpM3
  - 9 = TOON1 (VocF1)
  - 10 = TOON2 (VocF2)
  - 11 = TOON3 (VocF3)
  - 12 = TOON4 (VocM1)
  - 13 = TOON5 (VocM2)
  - 14 = TOON6 (VocM3)
  
- Sound_Name: The sound name that the participant hear

- Sound: The sound that the participant hear (ExpF1, ExpF2, ExpF3, ExpM1, ExpM2, ExpM3, VocF1, VocF2, VocF3, VocM1, VocM2 or VocM3)


```{r}
tmp <- df # Create a temporary file based on df

names(tmp)[1] <- "Ppt_Response_Nb"
tmp <- tmp %>% mutate(Ppt_Response_Nb = replace(Ppt_Response_Nb, X4 == 3, "NoResponse"))

tmp <- tmp %>% mutate(Ppt_Response = case_when(Ppt_Response_Nb == 1 & X4 != 3 ~ "g",
                                               Ppt_Response_Nb == 2 & X4 != 3 ~ "b",
                                               Ppt_Response_Nb == 3 & X4 != 3 ~ "h",
                                               Ppt_Response_Nb == 4 & X4 != 3 ~ "y", 
                                               X4 == 3 ~ "NoResponse"))

warning("If participant didn't give a response during the response time window (<1500ms), we assign Ppt_Response to 'NoResponse'. It's the same for the variable Ppt_Response_Nb")


names(tmp)[2] <- "Catego_Key_Response"
names(tmp)[3] <- "Key_Response_Nb"
names(tmp)[4] <- "Response_Status"
names(tmp)[5] <- "Target_Position"
names(tmp)[6] <- "Target_Type"
names(tmp)[7] <- "Target_Color"

names(tmp)[8] <- "Cueing_Status"
tmp <- tmp %>% mutate(Cueing_Validity = case_when(Cueing_Status == "Same" ~ "Valid",
                                                  Cueing_Status == "Different" ~ "Invalid",
                                                  Cueing_Status == "NoLocation" ~ "NoValidity"))

names(tmp)[9] <- "Cue_Position"
names(tmp)[10] <- "Cue_Color"
names(tmp)[11] <- "Congruency"
names(tmp)[12] <- "RT"
names(tmp)[13] <- "Blockname"

tmp <- tmp %>% mutate(Block = case_when(Blockname == "Training_Red" ~ "Training",
                                        Blockname == "Training_Green" ~ "Training",
                                        Blockname == "Control_Red" ~ "Control",
                                        Blockname == "Control_Green" ~ "Control",
                                        grepl('^Trial', Blockname)&grepl('Threat', Blockname) ~ "Threat",
                                        grepl('^Trial', Blockname)&grepl('Scream', Blockname) ~ "Scream",
                                        grepl('^Trial', Blockname)&(grepl('RedToon', Blockname)|grepl('GreenToon', Blockname)) ~ "Toon",
                                        grepl('TrialToon', Blockname) ~ "Vocalization",
                                        Blockname == "ScaleControl" ~ "Scale",
                                        Blockname == "ScaleThreat" ~ "Scale",
                                        Blockname == "ScaleToon" ~ "Scale"))

TrialDistrib <- table(tmp$Block) # create a table with the total number of trials of each type
TrialNumber <- TrialDistrib/258  # create a table with the number of trials of each type per participant
Nb_Ppt<-nlevels(df$response_id) # Calculate the total number of participants
x <- c(1:7)

# Give the number of trials for each type of trials and the total number of trials in the overall sample 
for (i in x) {
  Text<- paste("Le total des essais dans le block", names(TrialDistrib)[[i]], "pour n =", Nb_Ppt, "participant.e.s effectuant", TrialNumber[[i]], "essais est", TrialDistrib[[i]])
  print(Text)
}


names(tmp)[14] <- "Taskname"
names(tmp)[15] <- "Order"
tmp <- tmp %>% mutate(Blockorder = case_when(Order == "1" ~ "ThreatFirst_Red",
                                             Order == "2" ~ "ThreatFirst_Green"))

names(tmp)[16] <- "SOA"
names(tmp)[17] <- "Task"

names(tmp)[18] <- "Emotion_Rating"
tmp <- tmp %>% mutate(Emotion_Rating = replace(Emotion_Rating, Emotion_Rating == -1, "NoResponse"))

####STOP HERE !!!!
warning("The scale is a 1 to 7 likert scale, but if participant didn't give a response during the response time window (<30s), we assign Emotion_Rating to 'NoResponse'.")
print(paste("There is", table(tmp$Emotion_Rating)[[1]], "cells that contain a -1 value in the overall set of responses"))

names(tmp)[19] <- "Emotion_Type"
tmp <- tmp %>% mutate(Emotion = case_when(Emotion_Type == "Angoisse" ~ "Anxious",
                                          Emotion_Type == "Calme" ~ "Calm",
                                          grepl('^Col', Emotion_Type) ~ "Angry",
                                          Emotion_Type == "Deprime" ~ "Depressed",
                                          Emotion_Type == "Joie" ~ "Happy",
                                          Emotion_Type == "Nervosite" ~ "Nervous",
                                          Emotion_Type == "Stress" ~ "Stressed",
                                          Emotion_Type == "Tension" ~ "Tense",))


names(tmp)[20] <- "Sound_Nb"
names(tmp)[21] <- "Sound_Name"
tmp <- tmp %>% mutate(Sound = case_when(Sound_Nb == "3" ~ "ExpF1",
                                        Sound_Nb == "4" ~ "ExpF2",
                                        Sound_Nb == "5" ~ "ExpF3",
                                        Sound_Nb == "6" ~ "ExpM1",
                                        Sound_Nb == "7" ~ "ExpM2",
                                        Sound_Nb == "8" ~ "ExpM3",
                                        Sound_Nb == "9" ~ "VocF1",
                                        Sound_Nb == "10" ~ "VocF2",
                                        Sound_Nb == "11" ~ "VocF3",
                                        Sound_Nb == "12" ~ "VocM1",
                                        Sound_Nb == "13" ~ "VocM2",
                                        Sound_Nb == "14" ~ "VocM3",))

df <- tmp

rm(list=setdiff(ls(), c("df"))) # clear workspace except the data frame
```

### Calculate Anxiety score
#### Converting rows in columns

```{r}
tmp <- df

#Fear <- filter(tmp, !is.na(tmp$Emotion_Rating)) ## Create a dataframe which only contains participant ratings on emotions

# Create a data frame converting emotion ratings in column instead of rows
## For the control Block

# dt_Emotion <- tmp %>% filter(grepl(pattern =  "Scale", Blockname))
# 
# dt_Emotion <- dt_Emotion %>% 
#   group_by(Emotion) %>% 
#   mutate(id = response_id) %>% 
#   pivot_wider(
#     names_from = c(Emotion, Blockname),
#     values_from = c(Emotion_Rating)
#   )

dt_Control <- filter(tmp, Blockname == "ScaleControl")

dt_Control <- dt_Control %>% 
  group_by(Emotion) %>% 
  mutate(id = response_id) %>% 
  pivot_wider(
    names_from = Emotion,
    values_from = c(Emotion_Rating)
  )

dt_Control <- select(dt_Control, Blockname, Taskname, Task, response_id, Block, Angry, Calm, Anxious, Nervous, Happy, Tense, Stressed, Depressed)

dt_Control <- dt_Control %>% 
   group_by(Blockname, Taskname, Task, response_id, Block) %>% 
   summarize_all(sum, na.rm = TRUE)


## For the Threat Block

dt_Threat <- filter(tmp, Blockname == "ScaleThreat")

dt_Threat <- dt_Threat %>% 
  group_by(Emotion) %>% 
  mutate(id = response_id) %>% 
  pivot_wider(
    names_from = Emotion,
    values_from = c(Emotion_Rating)
  )

dt_Threat <- select(dt_Threat, Blockname, Taskname, Task, response_id, Block, Angry, Calm, Anxious, Nervous, Happy, Tense, Stressed, Depressed)

dt_Threat <- dt_Threat %>% 
   group_by(Blockname, Taskname, Task, response_id, Block) %>% 
   summarize_all(sum, na.rm = TRUE)


## For the Toon Block

dt_Toon <- filter(tmp, Blockname == "ScaleToon")

dt_Toon <- dt_Toon %>% 
  group_by(Emotion) %>% 
  mutate(id = response_id) %>% 
  pivot_wider(
    names_from = Emotion,
    values_from = c(Emotion_Rating)
  )

dt_Toon <- select(dt_Toon, Blockname, Taskname, Task, response_id, Block, Angry, Calm, Anxious, Nervous, Happy, Tense, Stressed, Depressed)

dt_Toon <- dt_Toon %>% 
   group_by(Blockname, Taskname, Task, response_id, Block) %>% 
   summarize_all(sum, na.rm = TRUE)


# Combine these three data frame in a single one
Anxiety_Scale <- rbind(dt_Control, dt_Threat, dt_Toon)

sum(Anxiety_Scale[,6:13]==-1) # The number of no responses (= -1) to the anxiety scale
# length(which(Anxiety_Scale$Angry==-1)) # To count the number of no response only for one emotion (i.e: Angry)

# Replace the -1 rating (=no response) to "NA"
Anxiety_Scale <- Anxiety_Scale %>% mutate(Angry = replace(Angry, Angry==-1, NA),
                                          Calm = replace(Calm, Calm==-1, NA),
                                          Anxious = replace(Anxious, Anxious==-1, NA),
                                          Nervous = replace(Nervous, Nervous==-1, NA),
                                          Happy = replace(Happy, Happy==-1, NA),
                                          Tense = replace(Tense, Tense==-1, NA),
                                          Stressed = replace(Stressed, Stressed==-1, NA),
                                          Depressed = replace(Depressed, Depressed==-1, NA),)

warning("Les non-reponses des participant.e.s (= -1) ont été remplacée par des valeurs manquantes (NA)")

# Reverse the calm item
Anxiety_Scale <- Anxiety_Scale %>% mutate(Calm_Recod = (8-Calm))

dt_Control <- dt_Control %>% mutate(Calm_Recod = (8-Calm))
dt_Threat <- dt_Threat %>% mutate(Calm_Recod = (8-Calm))
dt_Toon <- dt_Toon %>% mutate(Calm_Recod = (8-Calm))

# Associate each participant row to its block
Anxiety_Scale <- Anxiety_Scale %>% mutate(Block = case_when(Blockname == "ScaleControl" ~ "Control",
                                                            Blockname == "ScaleThreat" ~ "Threat",
                                                            Blockname == "ScaleToon" ~ "Toon"))


rm(list=setdiff(ls(), c("df","Anxiety_Scale"))) # clear workspace except the data frame and the "Anxiety_Scale" dataframe
```


#### Calculation of a factorial score
Here we want to calculate a factorial score for each participant and for each block based on the five items of anxiety feelings during the experiment

```{r}
tmp <- na.omit(Anxiety_Scale)
warning("Here, we have removed rows with NA")

# Check if it is possible to agregate theses five measure (anxious, nervous, calm, tense, stressed) in an unique factor : 
dt1_Factor<- na.omit(tmp[,c(6,8:14)])

# Some codes if we want to look if the factorial structure of this scale is the same between different blocks
#dtCtrl_Factor <- na.omit(dt_Control[,c(6,8:14)])
#dtThreat_Factor <- na.omit(dt_Threat[,c(6,8:14)])
#dtToon_Factor <- na.omit(dt_Toon[,c(6,8:14)])


EFA_dt1 <- factanal(dt1_Factor, factors=2, rotation = "promax") # Promax = Oblique rotation
print(EFA_dt1, digits = 2, cutoff = .3)
rm(dt1_Factor,EFA_dt1)
## We couldn't agregate "Calm" item to other items of anxiety because it is not loaded with the same factor
# Moreover, items "angry" and "depressed" load with the anxiety factor but to a lesser degree, so we decided not to agregate these items in our factorial score  according to our preregistration

## Now we calculate a factorial score from these 4 measure of stress
dt2_Factor <- na.omit(tmp[,c(6,9,11,12)])
FactorialScore <- fa(dt2_Factor, nfactors=1, rotate = "promax", scores = "Bartlett")
tmp$Fear_Score<-FactorialScore$scores # Assign a threat score to each ppt calculated on the 4 measures of stress
tmp$Fear_Score <- as.numeric(tmp$Fear_Score)

# Calculating a mean rather than a factorial score
tmp <- tmp %>% mutate(Fear_Mean = mean(Anxious, Nervous, Stressed, Tense))

# Calculate the correlation between the factorial or the mean score of each participant on these 4 items
cor.test(tmp$Fear_Score,tmp$Fear_Mean)

Anxiety_Scale <- tmp

rm(list=setdiff(ls(), c("df","Anxiety_Scale"))) # clear workspace except the data frame and the "Anxiety_Scale" dataframe
```

## Questionnaire dataframe
Associate the data from the experiment to the data from the questionnaire



```{r}
tmp <- df

tmp2 <- data <- read_csv("Data/data.csv")
#tmp2$Ppt <- NA
warning("j'ai pas encore pris le temps de faire le code book pour les variables que je suis en train de créer...!")

names(tmp2)[1] <- "Participant"
names(tmp2)[2] <- "PTSD1"
names(tmp2)[3] <- "PTSD2"
names(tmp2)[4] <- "PTSD3"
names(tmp2)[5] <- "PTSD4"
names(tmp2)[6] <- "PTSD5"
names(tmp2)[7] <- "PTSD6"
names(tmp2)[8] <- "PTSD7"
names(tmp2)[9] <- "PTSD8"
names(tmp2)[10] <- "PTSD9"
names(tmp2)[11] <- "PTSD10"
names(tmp2)[12] <- "PTSD11"
names(tmp2)[13] <- "PTSD12"
names(tmp2)[14] <- "PTSD13"
names(tmp2)[15] <- "PTSD14"
names(tmp2)[16] <- "PTSD15"
names(tmp2)[17] <- "PTSD16"
names(tmp2)[18] <- "PTSD17"
names(tmp2)[19] <- "PTSD_Score"

# PTSD diagnostic in accordance to the threshold of 61 on a 1 to 5 point scale (or 44 on a 0 to 4 point scale)
tmp2 <- tmp2 %>% mutate(PTSD_Diag = case_when(PTSD_Score >= 61  ~ "Diag", PTSD1 <= 60 ~ "NoDiag"))


names(tmp2)[20] <- "Angry_pretest"
names(tmp2)[21] <- "Anxious_pretest"
names(tmp2)[22] <- "Happy_pretest"
names(tmp2)[23] <- "Depressed_pretest"
names(tmp2)[24] <- "Tense_pretest"
names(tmp2)[25] <- "Calm_pretest"
names(tmp2)[26] <- "Stressed_pretest"
names(tmp2)[27] <- "Nervous_pretest"


tmp2 <- tmp2 %>% mutate(Calm_Recod_Pretest = (8-Calm_pretest))

dt1_Factor<- na.omit(tmp2[,c(20:24,26:27, 50)])
EFA_dt1 <- factanal(dt1_Factor, factors=2, rotation = "promax") # Promax = Oblique rotation
print(EFA_dt1, digits = 2, cutoff = .3)
rm(dt1_Factor,EFA_dt1)

dt2_Factor <- na.omit(tmp2[,c(21,24,26,27)])
FactorialScore <- fa(dt2_Factor, nfactors=1, rotate = "promax", scores = "Bartlett")
tmp2$Fear_Score_Pretest<-FactorialScore$scores # Assign a threat score to each ppt calculated on the 4 measures of stress
tmp2$Fear_Score_Pretest <- as.numeric(tmp2$Fear_Score_Pretest)
rm(dt2_Factor,FactorialScore)

# Calculating a mean rather than a factorial score
tmp2$Fear_Mean_Pretest<- apply(tmp2[,c(21,24,26,27)], 1, mean)
cor.test(tmp2$Fear_Score_Pretest,tmp2$Fear_Mean_Pretest)

#tmp2 <- tmp2 %>% mutate(Fear_Mean_Pretest = mean(Anxious_pretest, Tense_pretest, Stressed_pretest, Nervous_pretest))
warning("Pk mutate ne fonctionne pas ici pour calculer la moyenne ???")




names(tmp2)[28] <- "Sound_Calibration"
names(tmp2)[29] <- "Sound_Problem"
names(tmp2)[30] <- "Task_Type"

tmp2 <- tmp2 %>% mutate(Condition = case_when(Task_Type == "1" ~ "Controlability",
                                              Task_Type == "2" ~ "Random"))


names(tmp2)[31] <- "Exp_Controlability"
names(tmp2)[32] <- "Exp_Random"

tmp2 <- tmp2 %>% mutate(Ppt = case_when(!is.na(Exp_Controlability)~tmp2$Exp_Controlability,
                                        !is.na(Exp_Random)~ tmp2$Exp_Random))


names(tmp2)[33] <- "Check_Sound"
names(tmp2)[34] <- "Check_Uncomfort"
names(tmp2)[35] <- "Check_Volume"

names(tmp2)[36] <- "Threat_Scream1"
names(tmp2)[37] <- "Threat_Scream2"
names(tmp2)[38] <- "Threat_Vocal1"
names(tmp2)[39] <- "Threat_Vocal2"


names(tmp2)[40] <- "Check_Controlability1"
names(tmp2)[41] <- "Check_Controlability2"
names(tmp2)[42] <- "Check_Random1"
names(tmp2)[43] <- "Check_Random2"

names(tmp2)[44] <- "Age"
names(tmp2)[45] <- "Gender"
names(tmp2)[46] <- "TIME_Start"
names(tmp2)[47] <- "TIME_End"
names(tmp2)[48] <- "TIME_Total"


tmp <- dplyr::left_join(tmp, tmp2, by="Ppt")
tmp <- dplyr::left_join(tmp, Anxiety_Scale, by= c("response_id","Block"))


df <- tmp

rm(list=setdiff(ls(), c("df"))) # clear workspace except the data frame
```

## Other cleanings

```{r}
tmp <- df

tmp <- tmp %>% filter(Block != "Training" &
                        Block != "Vocalization" &
                        Block != "Scream" &
                        Block != "Scale")

warning(paste("Ici, nous supprimons toutes les lignes de l'expérience qui ne mesurent pas des temps de réaction. Le total des lignes supprimées est n =", (table(df$Block)[[2]] + table(df$Block)[[3]] + table(df$Block)[[6]] + table(df$Block)[[7]])))

# Check the number of removed rows
near((nrow(tmp) + table(df$Block)[[2]] + table(df$Block)[[3]] + table(df$Block)[[6]] + table(df$Block)[[7]]),nrow(df))

tmp <- tmp %>% filter(Response_Status==1)

warning(paste("Ici, nous supprimons toutes les lignes de l'expérience ou les participant.e.s ont fait une erreur ou n'ont pas répondu. Le total des lignes supprimées est n =", (111456-93491)))

df <- tmp

rm(list=setdiff(ls(), c("df"))) # clear workspace except the data frame
```


# Analysis

## Variable check 

### Anxiety

```{r}

tmp <- Anxiety_Scale
tmp <- tmp %>% mutate(Block_Recod = case_when(Blockname == "ScaleControl" ~ -1,
                                              Blockname == "ScaleToon" ~ -1,
                                              Blockname == "ScaleThreat" ~ 2))


Test <- lmer(Fear_Score ~ Block_Recod + + (1|response_id), data = tmp)
summary(Test)
Mean <- tmp %>% 
  group_by(Blockname) %>%
  summarise(mean=mean(Fear_Score), sd=sd(Fear_Score), n=length(response_id))
view(Mean)

```

## Main analysis

```{r}
tmp <- df

tmp <- tmp %>%filter(Cueing_Validity != "NoValidity")

warning("Attention, ici, nous avons supprimé tous les essais ou aucun indice n'était presenté pour simplifier les analyses.")

tmp <- tmp %>% mutate(Block_Recod = case_when(Block == "Control" ~ -0.5,
                                              Block == "Toon" ~ 0,
                                              Block == "Threat" ~ 0.5))

tmp <- tmp %>% mutate(Congruency_Recod = case_when(Congruency == "Incongruent" ~ -0.5,
                                                   Congruency == "Congruent" ~ 0.5))

tmp <- tmp %>% mutate(Cueing_Validity_Recod = case_when(Cueing_Validity == "Invalid" ~ -0.5,
                                                        Cueing_Validity == "Valid" ~ 0.5))

tmp <- tmp %>% mutate(Condition_Recod = case_when(Condition == "Controlability" ~ -0.5,
                                                  Condition == "Random" ~ 0.5))


Test <- lmer(RT ~ Congruency_Recod*Cueing_Validity_Recod*Block_Recod + (1|response_id), data = tmp)
summary(Test)


tmp2 <- tmp %>% filter(Block != "Toon")
Test <- lmer(RT ~ Congruency_Recod*Cueing_Validity_Recod*Block_Recod + (1|response_id), data = tmp2)
summary(Test)
Mean <- tmp2 %>% 
  group_by(Congruency, Cueing_Validity, Block) %>%
  summarise(mean=mean(RT), sd=sd(RT), n=length(response_id))
view(Mean)

# Controlability effect: comparison between Threat controlability and Threat random conditions
tmp3 <- tmp %>% filter(Block == "Threat") # Remove the control and toon conditions
CtrlEffect <- lmer(RT ~ Congruency_Recod*Cueing_Validity_Recod*Condition_Recod + (1|response_id), data = tmp3)
summary(CtrlEffect)
MeanCtrl <- tmp3 %>% 
  group_by(Congruency, Cueing_Validity, Condition) %>%
  summarise(mean=mean(RT), sd=sd(RT), n=length(response_id))
view(MeanCtrl)

# Controlability effect: comparison between control and threat controlability conditions
tmp4 <- tmp2 %>% filter(Condition == "Controlability") # Remove the control and toon conditions
CtrlEffect2 <- lmer(RT ~ Congruency_Recod*Cueing_Validity_Recod*Block_Recod + (1|response_id), data = tmp4)
summary(CtrlEffect2)
MeanCtrl2 <- tmp4 %>% 
  group_by(Congruency, Cueing_Validity, Block) %>%
  summarise(mean=mean(RT), sd=sd(RT), n=length(response_id))
view(MeanCtrl2)

```

 ctrl +Maj + C : add comments # on multiple lines

ctrl + I : aligner les lignes